---
title: "Goose model testing"
author: "The awesome Goose management Team"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, cache=FALSE, tidy=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE)  # fig.path='figs/'
```


```{r load, message=FALSE, include=FALSE}
library(ralmass)
library(tidyverse)
library(lubridate)
library(readxl)
library(knitr)
library(broom)
library(sf)
library(viridis)
library(ggthemes)
library(RColorBrewer)
library(ggmap)
library(pander)
library(assertr)
library(fs)
library(colorblindr)
library(rebus)
library(patchwork)
library(here)

#resultpath <- path_home("almass", "run-directory")
resultpath <- "F:/GooseTests/run-directory"
git_dir <- "F:/GooseTests/"
runinfo = readLines(path(resultpath, 'BatchALMaSS.ini'))
simyears = as.numeric(runinfo[length(runinfo) - 1])
windowsFonts(Arial=windowsFont("TT Arial")) 

sim = ''
extention = '.res'
```

This is a workdocument for collecting output from the **ALMaSS** Goose management model.

Document compiled: `r Sys.time()`

Number of simulation years: `r simyears` (only valid for commandline runs)

Results read from: `r resultpath`

Date stamp on ALMaSS exe file: `r file.info(paste0(resultpath, 'ALMaSS_CmdLine.exe'))$mtime` 

## Notes to run
`r Sys.Date()`. 

Still with plowing postponed, but also with harvest postponed.


## Available forage
```{r forage, fig.width=14, fig.height=16}
coltypes <- "iii--iiiiiidiiidiiidddcddccc"
read_tsv(path(resultpath, "GooseFieldForageData.txt"), 
         col_types = coltypes) %>% 
  mutate(day = day - 365L,
         date = as.Date(day, origin = as.Date("2009-01-01")),
         month = month(date)) %>% 
  filter(month %in% c(8:12,1:3),
         geese > 0) %>% 
  ClassifyHabitatUse(species = 'goose', timed = TRUE) -> forage

# First melt the numbers:
forage %>%
  dplyr::select(day,
                polyref,
                grain,
                maize,
                barnacle,
                pinkfoot,
                greylag) %>% 
  gather(key = species,
          value = number,
          c(barnacle, pinkfoot, greylag)) -> numbers_tb
  
# Then melt the grass forage
forage %>%
  dplyr::select(day, 
                polyref,
                grass_pinkfoot,
                grass_barnacle,
                grass_greylag) %>% 
  gather_(key_col = "species",
          value_col = "KjAvailable",
          gather_cols = c("grass_pinkfoot", "grass_barnacle", "grass_greylag")) %>% 
  mutate(species = str_sub(species, start = 7)) -> grassforage_tb

# Then merge and plot
left_join(numbers_tb, grassforage_tb, by = c("day", "polyref", "species")) %>% 
  rename(grass = KjAvailable) %>% 
  gather_(key_col = "type", value_col = "KjAvailable", gather_cols = c('grain', 'maize', 'grass')) %>% 
  filter(number > 0, KjAvailable > 0.01) %>% 
  ggplot(aes(day, KjAvailable)) +
  geom_point(alpha = 1/10, aes(size = log10(number))) +
  facet_grid(type~species, scales = 'free_y') + theme_bw()
```
Plot characters and lines all have the same grey color, so black chunks are the result of overplotting. Only fields where the geese where actually foraging on are plotted. Dots are scaled to the logarithm of the numbers present on a field.
Turn off this chunk to save time when the document complies.

```{r}
barnacle_max <- 13.4626
pinkfoot_max <- 16.6134
greylag_max <- 24.3769

forage %>% 
  select(day, polyref, veg_type_chr, veg_height) %>% 
  dplyr::filter(str_detect(veg_type_chr, "Gra")) %>% 
  group_by(day, veg_type_chr) %>% 
  summarise(height = mean(veg_height),
            low = height - sd(veg_height),
            up = height + sd(veg_height)) %>% 
  mutate(low = if_else(is.na(low), height, low ),
         up = if_else(is.na(up), height, up)) %>% 
  ungroup() %>% 
  ggplot(aes(day, height, fill = veg_type_chr)) +
  geom_line(aes(color = veg_type_chr)) + 
  geom_ribbon(aes(ymin = low, ymax = up), alpha = 0.3) +
  labs(title = "Vegetation heights",
       subtitle = "Grassy vegation types",
       y = "Mean vegetation height (+-SD)",
       caption = "Dark grey horizontal lines showing the max\nwhere intake is possible for each species") +
  scale_fill_discrete(guide = guide_legend(title = "Veg type")) +
  scale_color_discrete(guide = guide_legend(title = "Veg type")) +
  hrbrthemes::theme_ipsum_ps() +
  geom_hline(yintercept = barnacle_max, color = "darkgrey") +
  annotate("text", x = 442, y = barnacle_max - 3, label = "Barnacle", color = "darkgrey") +
  geom_hline(yintercept = pinkfoot_max, color = "darkgrey") +
  annotate("text", x = 435, y = pinkfoot_max + 3, label = "Pinkfoot", color = "darkgrey") +
  geom_hline(yintercept = greylag_max, color = "darkgrey") +
  annotate("text", x = 435, y = greylag_max + 4, label = "Greylag", color = "darkgrey")

# Not Grass
forage %>% 
  select(day, polyref, veg_type_chr, veg_height) %>% 
  filter(!str_detect(veg_type_chr, "Gra")) %>% 
  group_by(day, veg_type_chr) %>% 
  summarise(height = mean(veg_height),
            low = height - sd(veg_height),
            up = height + sd(veg_height)) %>% 
  mutate(low = if_else(is.na(low), height, low ),
         up = if_else(is.na(up), height, up)) %>% 
  ungroup() %>% 
  ggplot(aes(day, height, fill = veg_type_chr)) +
  geom_line(aes(color = veg_type_chr)) + 
  geom_ribbon(aes(ymin = low, ymax = up), alpha = 0.3) +
  labs(title = "Vegetation heights",
       subtitle = "Non-grassy vegation types",
       y = "Mean vegetation height (+-SD)",
       caption = "Dark grey horizontal lines showing the max\nwhere intake is possible for each species") +
  scale_fill_discrete(guide = guide_legend(title = "Veg type")) +
  scale_color_discrete(guide = guide_legend(title = "Veg type")) +
  hrbrthemes::theme_ipsum_ps() +
  geom_hline(yintercept = barnacle_max, color = "darkgrey") +
  annotate("text", x = 432, y = barnacle_max - 3, label = "Barnacle", color = "darkgrey") +
  geom_hline(yintercept = pinkfoot_max, color = "darkgrey") +
  annotate("text", x = 435, y = pinkfoot_max + 3, label = "Pinkfoot", color = "darkgrey") +
  geom_hline(yintercept = greylag_max, color = "darkgrey") +
  annotate("text", x = 435, y = greylag_max + 4, label = "Greylag", color = "darkgrey")
```


```{r mean_grain, fig.width=10, message=FALSE, eval=FALSE}
forage %>%
  filter(grain > 0.0) %>% 
    mutate(grain_kj_pf = map_dbl(grain, .f = get_func_resp, species = "pinkfoot", resp = resp),
         grain_kj_gl = map_dbl(grain, .f = get_func_resp, species = "greylag", resp = resp),
         grain_kj_bn = map_dbl(grain, .f = get_func_resp, species = "barnacle", resp = resp)) %>% 
  select(Season, day, starts_with("grain_")) %>% 
  group_by(season, day) %>% 
  summarise(avg_kj_pf = mean(grain_kj_pf),
            avg_kj_gl = mean(grain_kj_gl),
            avg_kj_bn = mean(grain_kj_bn)) %>% 
  tidyr::gather(type, kJ, -day, -season) %>% 
    ggplot(aes(day, kJ)) +
    geom_line(aes(color = type)) + 
    geom_point(aes(color = type)) +
    scale_color_colorblind() + 
    facet_wrap(~season) +
    theme_bw() + 
    ggtitle("Mean daily kJ available from grain",
            subtitle = "kJ before flock size dependent feeding time adjustment \nOnly fields with geese")
```

```{r gg_line_ribbon}
gg_line_ribbon <- function(data, var, var_se) {
  quo_var <- enquo(var)
  quo_var_se <- enquo(var_se)
  var_up <- paste0(quo_name(quo_var), "_up")
  var_low <- paste0(quo_name(quo_var), "_low")
  data %>% 
    mutate(!!var_up := !!quo_var + !!quo_var_se,
           !!var_low := !!quo_var - !!quo_var_se) %>% 
    ggplot(aes_q(quote(date), quo_var, fill = quote(species))) +
    geom_line(aes_q(color = quote(species))) + 
    geom_ribbon(aes_string(ymin = var_low, ymax = var_up), alpha = 0.3) + 
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_OkabeIto() +
    scale_fill_OkabeIto() +
    hrbrthemes::theme_ipsum_ps()
}
```



## Weight development
```{r weight, fig.width=10, message=FALSE}
read_tsv(path(resultpath, "GooseWeightStats.txt"),
                   col_types = "iiicddi") %>% 
    dplyr::filter(mean_weight != -1) %>% 
    mutate(Date = as.Date(day - 365, origin = as.Date("2009-01-01")),
           SEupper = mean_weight + mean_weight_se,
           SElower = mean_weight - mean_weight_se) -> weights

weights %>% 
  ggplot(aes(Date, mean_weight)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = SElower, ymax = SEupper), width = 0.5) +
  facet_wrap(~species, scales = "free_y") 
  
  
read_tsv(path(git_dir,  "/ALMaSS_inputs/GooseManagement/Vejlerne/APIdata.txt"),
         col_types = "Dcdd") %>% 
  dplyr::filter(Date > ymd("2010-08-01"),
	        Date < ymd("2015-05-31")) %>% 
	  mutate(week = week(Date)) %>% 
	  group_by(week) %>% 
	  summarise(mean_weight_field = mean(Weight)) -> field

weights %>% 
  dplyr::filter(species == "pinkfoot",
	       mean_weight != -1) %>% 
	dplyr::filter(month(Date) %in% c(9:12,1:3)) %>% 
	group_by(season) %>% 
	mutate(week = get_week(day_in_year)) -> weights

fits <- calc_weight_fit(weights, field)
```

Pinkfoot(s) were `r round(fits, 2)`.

## Distance flown
```{r flightdistance, fig.height=6, fig.width=10}
read_tsv(path(resultpath, 'GooseEnergeticsData.txt'),
                            col_types = "iicddddddddi") %>% 
  mutate(day = day - 365,
         date = as.Date(day, origin = as.Date('2009-01-01'))) %>% 
  mutate_at(vars(contains("distance")), funs( . / 1000)) -> energy

energy %>% 
  filter(flight_distance > 0) %>% 
  gg_line_ribbon(flight_distance, flight_distance_se) +
  labs(title = "Seasonal flight distance",
       y = "Mean distance flown per day (km)")
```

## Foraging time
```{r fulltime, fig.height=5, fig.width=10}
energy %>%
  gg_line_ribbon(foraging_time, foraging_time_se) +
  geom_line(aes(date, day_length), color = "darkgrey") +
  annotate("text", x = as.Date("2009-09-13"), y = 925, label = "day length", color = "Darkgrey") +
  labs(title = "Seasonal foraging time",
       y = "Foraging time (minutes)")
```

## Daily energy budget
```{r m_DEB}
energy %>% 
  gg_line_ribbon(daily_energy_budget, daily_energy_budget_se) + 
  labs(title = "Seasonal energy budget",
       y = "Daily energy budget",
       subtitle = "Daily energy expenditure excluding flight")
```

## Daily energy balance
```{r DEE}
energy %>% 
  gg_line_ribbon(daily_energy_balance, daily_energy_balance_se) +
  geom_abline(slope = 0, intercept = c(0.0), color = "darkgrey") +
  # scale_y_continuous(limits = c(-500, NA)) +
  labs(title = "Daily energy balance",
       y = "Average energy balance (kJ)") 
```


```{r forage_locations}
read_tsv(path(resultpath, "GooseIndLocCountStats.txt"), col_types = "iiicddi") %>% 
  mutate(date = as.Date(day - 365, origin = as.Date('2009-01-01'))) %>% 
  filter(n_forage_locs > -1) %>% 
  gg_line_ribbon(n_forage_locs, n_forage_locs_se) +
  scale_y_continuous(breaks = seq(0,2.5, by = 0.5)) +
  labs(title = "Number of forage locations",
       y = "Daily number of forage locations")
```

## Number of flocks per day

```{r flocknumbers, fig.width=10}
forage %>%
  select(day,
         greylag_timed,
         barnacle_timed,
         pinkfoot_timed,
         season) %>%
  gather(value = numbers,
          key = species,
          c(greylag_timed, barnacle_timed, pinkfoot_timed)) %>%
  filter(numbers > 0) %>%
  group_by(day, species) %>%
  mutate(N = n()) %>% 
  ungroup() %>% 
  mutate(species = str_sub(species, end=-7)) %>% 
  ggplot(aes(day, N)) +
  geom_line() +
  geom_point() +
  facet_wrap(~species, scales = 'free') +
  ylab('Flock numbers')
```

## AOR grid
```{r AOR_grid, fig.height=6, fig.width=10, message=FALSE}
# Define projection:
utm32 <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
# Define AOR grid size
grid_size = 1000
 
ext <- read_sf(here::here("data", "vejlerne-outline.gpkg")) %>% 
  st_transform(crs = "+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs") %>% 
    raster::extent()
# Define template raster
r1 <- raster::raster(nrows = 24000/grid_size, 
             ncols = 36000/grid_size,
             ext = ext,
             crs = "+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs")
# Get the default value for FL  
cfg <- readLines(path(resultpath, 'TIALMaSSConfig.cfg'))
defaultval = GetParamValue(param = "GOOSE_FOLLOWINGLIKELYHOOD_PF",
                           config = cfg)
# Make spatial object of xy dump file
polygons <- read_tsv(path(resultpath, "GooseXYDump.txt"), col_types = "iiiiii") %>% 
  UtmToALMaSS(long = "X", lat = "Y", toalmass = FALSE, map = "VejlerneBigMap") %>% 
  select(ALong, ALat) %>% 
  sp::SpatialPoints(proj4string = sp::CRS("+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs")) %>% 
  # Tally occurences in cells and plot
  raster::rasterize(y = r1, fun = "count") %>% 
  raster::rasterToPolygons() %>% 
  sp::spTransform(CRSobj = sp::CRS("+init=epsg:4326"))
# Get a map background
map <- st_read(here::here("data", "vejlerne-outline.gpkg"),
                 quiet = TRUE) %>% 
  st_transform(crs = "+init=epsg:4326") %>% 
  st_bbox() %>% 
  as.numeric() %>% 
  get_stamenmap(zoom = 11, maptype = "toner-lite")
# Ugly hack to make the plot work. Will be much nicer when geom_sf is fully implemented
# tmp <- tidy(fields)
tmp <- tidy(polygons)
tmp2 <- polygons@data
tmp2$id <- row.names(tmp2)
tmp3 <- left_join(tmp, tmp2)
# pdf(file = "C:/Users/lada/test.pdf")
ggmap(map) + 
  geom_polygon(data = tmp3, aes(long, lat, group = id, fill = layer)) + 
  scale_fill_gradient(guide = guide_legend(title = "Count")) +
  ggtitle("Grid cell occupancy - Pinkfeet",
          sub = paste0("Grid size = ", grid_size, "m. Followinglikelyhood ", defaultval))
# dev.off()
```

## AOR table
```{r AOR_table, message=FALSE}
dir_ls(path = resultpath) %>% 
  str_subset("AOR_[a-z]") -> aor_files

tibble(files = path_file(aor_files)) %>% 
  mutate(aor = map(files, ~ read_tsv(path(resultpath, .), col_types = "iiiiiiiiiii")),
         aor = map(aor, ~ tidy_aor(.)),
         species = str_sub(files, start = 5, end = -5)) %>% 
  select(-files) %>% 
  unnest() %>% 
  DT::datatable()  
```

## Numbers
```{r numbers, fig.height=6, fig.width=10}
read_tsv(path(resultpath, 'GoosePopulationData.txt'),
              col_types = "iiiiiiiid") %>% 
  mutate(day = day - 365) %>%
  PlotGoosePopulation()
```
\newpage

## Leave reason
```{r leavereason, fig.height=8, fig.width=10}
read_tsv(path(resultpath, 'GooseLeaveReasonStats.txt'), col_types = "iiicci") %>% 
  filter(n > 0) %>% 
  mutate(day = day - 365,
         species = str_extract(species_type, "[^_]*")) %>% 
  group_by(species, day, leave_reason) %>% 
  summarise(n = sum(n)) -> leavereason
if (nrow(leavereason) > 0) {
  ggplot(leavereason, aes(day, n)) + 
    geom_line(aes(color = leave_reason)) +
    facet_grid(leave_reason ~ species, scales = "free_y")
}
```

## Flock sizes
```{r flocks, fig.height=4, fig.width=10}
read_tsv(path(resultpath, "fieldobs_01112017.tsv"),
	         col_types = "cdTdiii") %>% 
  mutate(species = tolower(species)) %>% 
  select(species, numbers) %>% 
  mutate(type = "Fieldobs") -> flocks

# Timed counts:
forage %>% 
  dplyr::select(barnacle_timed, pinkfoot_timed, greylag_timed) %>% 
  gather_(key_col = 'species',
          value_col = 'numbers',
          gather_cols = c("barnacle_timed", "pinkfoot_timed", "greylag_timed")) %>% 
  filter(numbers != 0) %>% 
  mutate(type = "simulated") %>% 
  mutate(species = recode(species,
                          "barnacle_timed" = "barnacle",
                          "pinkfoot_timed" = "pinkfoot",
                          "greylag_timed" = "greylag")) %>%
  magrittr::set_names(tolower(names(.))) %>%
  bind_rows(flocks) -> flock_size_data

flock_size_data %>% 
  # mutate(numbers = log10(numbers)) %>%
  filter(species != "greylag") %>% 
  ggplot(aes(x = numbers, fill = type)) +
  geom_density(alpha = 0.5, colour = NA) +
  facet_grid(~ species, scales = 'free_x') +
  theme_bw()
# Calculate fit:
read_tsv(path(resultpath, "fieldobs_01112017.tsv"),
	         col_types = "cdTdiii") %>% 
    mutate(species = tolower(species)) %>% 
	  group_by(species) %>%
	  nest(.key = "observation") -> field_obs

forage %>% 
	  select(season,
	         date,
	         barnacle = barnacle_timed, 
	         pinkfoot = pinkfoot_timed) %>% 
	  gather(key = "species", value = "numbers", -one_of("season", "date")) %>% 
	  filter(numbers > 0,
	         between(week(date), 38, 44))  %>%
	  group_by(season, species) %>%
	  nest(.key = "simulation") %>% 
  	left_join(field_obs, by = "species") %>% 
	  mutate(fit = pmap_dbl(list(sim = simulation,
	                             obs = observation,
	                             var = "numbers", 
	                             measure = "KS"),
	                        .f = CalcFlockSizeFit),
	         fit_type = "flock_size") %>% 
	  select(season, species, fit, fit_type) -> result
```

The fits were:
```{r}
pander(result)
```

Forage Months: `r unique(forage$month)`

## Habitat use
```{r habitat, echo=FALSE, fig.height=11, fig.width=10, message=FALSE}
read_tsv(path(resultpath, "habitat-use-2014.tsv"),
	         col_types = "iicc") %>% 
  mutate(month = ifelse(month < 7L, month + 12L, month)) %>% 
	  group_by(month, species, habitat) %>% 
	  summarize(total = sum(N)) %>% 
	  mutate(use = total/sum(total)) %>% 
  ungroup() %>% 
  rename(habitat_use = habitat) -> field_data


# Plot settings    
cols <- c("Grass" = "#66C2A5",
          "Maize" = "#FC8D62",
          "Rape" = "#8DA0CB",
          "Stubble" = "#E78AC3",
          "WinterCereal" = "#A6D854")
x_scale <- scale_x_continuous(breaks = 9:15, 
                     labels = c("9", "10", "11", "12", "1", "2", "3"),
                     limits = c(8.5, 15.5))
field_data %>% 
  ggplot(aes(month, fill = habitat_use)) +
  geom_bar(aes(weight = total), position = 'fill') + 
  facet_wrap(~species, scales = "free_x") + 
  scale_fill_manual(values = cols, guide_legend(title = "Habitat")) +
  scale_y_continuous(labels = scales::percent) + 
  ylab("Use") + 
  x_scale +
  theme_fivethirtyeight() +
  ggtitle("Field data habitat use") -> fd_plot
  


# Strp the relevant columns and construct a habitat use data set
habpf <- forage %>% 
  dplyr::select(season, month, habitat_use = HabitatUsePF, numbers = pinkfoot_timed) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::group_by(season, month, habitat_use) %>% 
  dplyr::summarise(numbers = sum(numbers)) %>% 
  dplyr::mutate(species = "pinkfoot",
                prop = numbers/sum(numbers))

habgl <- forage %>% 
  dplyr::select(season, month, habitat_use = HabitatUseGL, numbers = greylag_timed) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::group_by(season, month, habitat_use) %>% 
  dplyr::summarise(numbers = sum(numbers)) %>% 
  dplyr::mutate(species = "greylag",
                prop = numbers/sum(numbers))

habbn <- forage %>% 
  dplyr::select(season, month, habitat_use = HabitatUseBN, numbers = barnacle_timed) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::group_by(season, month, habitat_use) %>% 
  dplyr::summarise(numbers = sum(numbers)) %>% 
  dplyr::mutate(species = "barnacle",
                prop = numbers/sum(numbers))

bind_rows(habpf, habgl, habbn) -> sim_data
  
# Combine this and plot  
sim_data %>%  
  ungroup() %>% 
  mutate(month = ifelse(month < 7L, month + 12L, month)) %>% 
  ggplot(aes(month, fill = habitat_use)) +
  geom_bar(aes(weight = numbers), position = "fill") + 
  facet_wrap(~species, scales = "free_x") + 
  scale_fill_manual(values = cols, guide_legend(title = "Habitat")) +
  scale_y_continuous(labels = scales::percent) + 
  ylab("Use") + 
  x_scale +
  theme_fivethirtyeight() +
  ggtitle("Simulated habitat use") -> s_plot

# New habuse
read_tsv(path(resultpath, "GooseHabitatUseStats.txt"), col_types = "iiicddddi") %>% 
  filter(count > 0) %>% 
  mutate(date = as.Date(day - 365, origin = as.Date("2009-01-01")),
         month = as.integer(month(date)),
         month = ifelse(month < 7L, month + 12L, month),
         month = month - 1L) %>% 
  select(-count, -day, -day_in_year, -date) %>%
  gather(key = habitat,
         value = use,
         -c(season, month, species))  %>% 
  mutate(habitat = case_when(habitat == "winter_cereal" ~ "WinterCereal",
                            habitat == "grain" ~ "Stubble",
                            habitat == "grass" ~ "Grass",
                            habitat == "maize" ~ "Maize",
                            TRUE ~ "foo")) %>% 
  
ggplot(aes(month, use)) +
  geom_col(aes(fill = habitat), position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  x_scale +
  facet_wrap(~species, scales = "free_x") +
  scale_fill_manual(values = cols, guide_legend(title = "Habitat")) +
  theme_fivethirtyeight() +
  labs(title = "Simulated type of intake") -> new_habuse

read_tsv(path(resultpath, "GooseHabitatUseFieldObsStats.txt"), col_types = "iiicddddi") %>%
  filter(count > 0) %>% 
  mutate(date = as.Date(day - 365, origin = as.Date("2009-01-01")),
         month = as.integer(month(date)),
         month = ifelse(month < 7L, month + 12L, month),
         month = month - 1L) %>% 
  select(-count, -day, -day_in_year, -date) %>%
  gather(key = habitat,
         value = use,
         -c(season, month, species))  %>% 
  mutate(habitat = case_when(habitat == "winter_cereal" ~ "WinterCereal",
                            habitat == "grain" ~ "Stubble",
                            habitat == "grass" ~ "Grass",
                            habitat == "maize" ~ "Maize",
                            TRUE ~ "foo")) %>% 
  
ggplot(aes(month, use)) +
  geom_col(aes(fill = habitat), position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  x_scale +
  facet_wrap(~species, scales = "free_x") +
  scale_fill_manual(values = cols, guide_legend(title = "Habitat")) +
  theme_fivethirtyeight() +
  labs(title = "Simulated habitat use (new version)") -> new_fieldobs_habuse

fd_plot / s_plot / new_habuse / new_fieldobs_habuse

# Calculate the fit:
calc_habuse_fit <- function(sim, obs) {
	  left_join(obs, sim,
	            by = c("species", "month", "habitat")) %>% 
	    replace_na(list(use.y = 0.0)) %>% 
	    group_by(species, month) %>% 
	    summarise(fit = sum((use.x - use.y)^2)) %>% 
	    group_by(species) %>% 
	    summarise(fit = sum(fit)/n_distinct(month)) %>% 
	    return()
}

read_tsv(path(resultpath, "habitat-use-2014.tsv"),
	         col_types = "iicc") %>% 
	  group_by(month, species, habitat) %>% 
	  summarize(total = sum(N)) %>% 
	  mutate(use = total/sum(total)) %>% 
	  select(-total) %>% 
	  list() -> observations
	  
	forage %>% 
	  select(barnacle = barnacle_timed,
	         pinkfoot = pinkfoot_timed, 
	         greylag = greylag_timed,
	         month,
	         season) %>% 
	  gather(key = species, value = N, -one_of("month", "season")) %>% 
	  pull(N) -> numbers
	forage %>% 
	  select(barnacle = HabitatUseBN,
	         pinkfoot = HabitatUsePF,
	         greylag = HabitatUseGL,
	         month,
	         season) %>% 
	  gather(key = species, value = habitat, -one_of("month", "season")) %>% 
	  add_column(N = numbers) %>% 
	  filter(N > 0) %>% 
	  verify(not_na(habitat)) %>% 
	  group_by(season, month, species, habitat) %>% 
	  summarize(total = sum(N)) %>% 
	  mutate(use = total/sum(total)) %>% 
	  select(-total) %>% 
	  group_by(season) %>% 
	  nest(.key = "simulation") %>% 
	  add_column(observations) %>% 
	  mutate(fit = map2(simulation, observations, calc_habuse_fit)) %>% 
	  select(season, fit) %>% 
	  unnest() %>% 
	  mutate(fit_type = "habitat_use") %>% 
	  select(season, species, fit, fit_type) -> result_habuse
	  
```


Fits were:

```{r eval=FALSE, include=FALSE}
result_habuse %>% 
  mutate(fit = 1- fit) %>% 
  pander()
```

## Distance from foraging sites to nearest roost
```{r distances, fig.height=6, fig.width=12, message=FALSE}
forage %>% 
  mutate(week = week(date)) %>% 
	  filter(between(week, 38, 44)) -> forage
forage %>% 	
	  select(barnacle = barnacle_timed,
	         pinkfoot = pinkfoot_timed, 
	         season) %>% 
	  gather(key = species, value = N, -season) %>% 
	  pull(N) -> numbers
forage %>% 
  select(season,
         barnacle = roost_dist_barnacle,
         pinkfoot = roost_dist_pinkfoot) %>% 
  gather(key = species, value = dist, -season) %>% 
  add_column(numbers) %>% 
  filter(numbers > 0) %>% 
  group_by(season, species) %>% 
  nest(.key = "simulation") %>% 
  left_join(field_obs, by = "species") %>% 
  mutate(fit = pmap_dbl(list(sim = simulation, 
                             obs = observation,
                             var = "dist", 
                             measure = "KS"),
                        .f = CalcFlockSizeFit),
         fit_type = "roost_dist") %>% 
  select(season, species, fit, fit_type) -> result_dist

forage %>% 
  select(week,
         barnacle = roost_dist_barnacle,
         Pinkfoot = roost_dist_pinkfoot) %>% 
  gather(key = species, value = dist, -week) %>% 
  add_column(numbers) %>% 
  filter(numbers > 0) %>% 
  group_by(species, week) %>% 
  summarise(mean_dist = weighted.mean(dist, numbers),
            type = "simulation") -> sim_weekly

field_obs %>% 
  unnest() %>% 
  group_by(species, week) %>% 
  summarise(mean_dist = weighted.mean(dist, numbers),
            type = "observation") -> fieldobs_weekly

length(unique(forage$season)) -> n_seasons

# Make a combined plot: 
bind_rows(sim_weekly, fieldobs_weekly) %>% 
  ungroup() %>% 
  ggplot(aes(week, mean_dist/1000)) + 
  geom_line(aes(color = species, linetype = type)) + 
  ggtitle("Mean weekly distance (km) from forage location to roost",
          subtitle = paste0("Simulated data is averaged over ", n_seasons, " seasons. Field observations are from 2015.")) +
  scale_color_colorblind() + 
  scale_x_continuous(breaks = seq(38, 44))+
  theme_fivethirtyeight() + 
  theme(axis.text = element_text(size = 12))
``` 

Fits were:
```{r }
pander(result_dist)
```

## Functional responses
```{r functional, fig.height=6, fig.width=10, echo=FALSE}
# Maize:
read_tsv(path(resultpath, "CurvePointsKJIntakeAtDiffMaizeDensities_BN.txt"),
          col_names = c("maize_density", "intake_rate"),
          col_types = "dd") -> maize_curve
maize_curve %>% 
    mutate(species = "barnacle") -> maize_barnacle
maize_curve %>% 
  mutate(species = "pinkfoot",
         intake_rate = intake_rate * 1.35) -> maize_pinkfoot
maize_curve %>% 
  mutate(species = "greylag",
         intake_rate = intake_rate * 1.64) -> maize_greylag
bind_rows(maize_barnacle, maize_pinkfoot, maize_greylag) %>% 
  ggplot(aes(maize_density, intake_rate)) +
  geom_line(aes(color = species)) +
  scale_color_OkabeIto() +
  scale_fill_OkabeIto() +
  hrbrthemes::theme_ipsum_ps() + 
  labs(title = "Maize intake rates",
       x = expression(paste('kJ/', m^2)),
       y = "kJ per min") -> maize_plot

# grain:
read_tsv(path(resultpath, "CurvePointsKJIntakeAtDiffGrainDensities_PF.txt"),
          col_names = c("grain_density", "intake_rate"),
          col_types = "dd") -> grain_curve
grain_curve %>% 
  mutate(species = "pinkfoot") -> grain_pinkfoot
grain_curve %>% 
  mutate(species = "greylag",
         intake_rate = intake_rate * 1.21) -> grain_greylag
grain_curve %>% 
    mutate(species = "barnacle",
      intake_rate = intake_rate * 0.74) -> grain_barnacle
bind_rows(grain_barnacle, grain_pinkfoot, grain_greylag) %>% 
  ggplot(aes(grain_density, intake_rate)) +
  geom_line(aes(color = species)) +
  scale_color_OkabeIto() +
  scale_fill_OkabeIto() +
  hrbrthemes::theme_ipsum_ps() + 
  labs(title = "grain intake rates",
       x = expression(paste('grain/', m^2)),
       y = "kJ per min") -> grain_plot

# Grass
dir_ls(resultpath) %>% 
  str_subset("GrassHeights") -> grass_files
tibble(files = grass_files) %>% 
  mutate(grass = map(files, ~ read_tsv(., col_types = "dd", col_names = c("grass_height", "intake_rate"))),
         species = str_sub(files, start = -6, end = -5)) %>% 
  select(-files) %>% 
  unnest() %>% 
  mutate(species = case_when(species == "BG" ~ "barnacle",
                             species == "PF" ~ "pinkfoot",
                             species == "GL" ~ "greylag",
                             TRUE ~ "foo")) %>% 
  ggplot(aes(grass_height, intake_rate)) +
  geom_line(aes(color = species)) +
  scale_color_OkabeIto() +
  scale_fill_OkabeIto() +
  hrbrthemes::theme_ipsum_ps() + 
  labs(title = "Grass intake rates",
       x = "Grass height (cm)",
       y = "kJ per min") -> grass_plot

# Feeding time
read_tsv(path(resultpath, 'CurvePointsFeedingTimePettifor_PF.txt'),
              col_types = "dd",
              col_names = c("flock_size", "feeding_time")) %>% 
  ggplot(aes(flock_size, feeding_time)) +
  geom_line() +
  ylim(c(0.5, 1)) +
  hrbrthemes::theme_ipsum_ps() + 
  labs(title = "Feeding time",
       x = "Flock size",
       y = "Feeding time") -> feeding_time

 (grass_plot + feeding_time) / (maize_plot + grain_plot)
```


## Weather data
```{r weather, echo=FALSE, fig.width=10}
read_tsv(path(resultpath, 'Weather1990.pre'),
         col_names = c("year", "month", "day", "temperature", "rain"),
         col_types = "iiid-d",
         skip = 1) %>% 
  unite(date, year, month, day, sep = "-", remove = FALSE) %>% 
  mutate(diy = as.integer(yday(date)),
         year = as.factor(year)) %>% 
  select(-date, -month, -day) %>% 
  gather(key = variable, value = value, -diy, -year) %>% 
  ggplot(aes(diy, value)) +
  geom_hline(yintercept = 0, color = "darkgrey") +
  geom_line(aes(color = year)) +
  facet_wrap(~variable, scales = "free") +
  
  scale_color_OkabeIto() +
  hrbrthemes::theme_ipsum_ps() + 
  labs(x = "day in year",
       y = "")
```

## Configs
```{r config, echo=FALSE}
ScipenDefault = getOption('scipen')  # In case it should be turned back again.
options(scipen = 99)  # To avoid scientific notation in the resulting file
if (file.exists(path(resultpath, "GooseConfig.txt"))) {
  configs = data.table::fread(path(resultpath, 'GooseConfig.txt'))
  kable(configs, caption = 'Config settings used in this run')
}

```

